The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-02-02 paper/ms.tex
Fixed MRD figure caption.

\begin{figure}
\includegraphics[width=\columnwidth]{MRD_normal.pdf}
\caption{Mass ratio distribution for our sample. The data was fit to both a histogram and a log-normal distribution. The histogram is shown in the solid blue blocks, with $1 \sigma$ uncertainties marked with error bars. The variance of the log-normal fit is shown with 500 samples from the posterior probability distribution for the parameters.}
\label{fig:mrd}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{MRD_normal.pdf}
\caption{Mass ratio distribution for our sample. The data was fit to both a histogram and a gaussian distribution. The histogram is shown in the solid blue blocks, with $1 \sigma$ uncertainties marked with error bars. The variance of the gaussian fit is shown with 500 samples from the posterior probability distribution for the parameters.}
\label{fig:mrd}
\end{figure}
